% Set up the document parameters, load moderncv
\documentclass[11pt,a4paper]{moderncv}
\usepackage[utf8]{inputenc}
\usepackage{verbatim}

% Casual template, green colouring
\moderncvtheme[green]{casual}

\nopagenumbers{}

% Personal information
\firstname{Christopher}
\familyname{Smith}
\mobile{+64 21 447 834}
\email{chris@nevermind.co.nz}
\extrainfo{\url{www.nevermind.co.nz}}
\quote{26 year-old technology enthusiast and professional}

\begin{document}
\maketitle

\section{Experience}
\cventry{2008--Present}{Software Developer}{Mighty Ape}{}{}{
I am working on web applications and related software including frontend, administration and backend software. I'm also responsible for administration of the network and all component systems. I architected, implemented and maintain the current application environment and am responsible for it's every day stability and security.
}
\cventry{2006--2008}{Support Engineer}{Comverse Ltd.}{}{}{
I was a Tier 3 support engineer for Comverse's messaging platform at Vodafone NZ. I handled severe issues escalated from Vodafone's support staff and day-to-day maintenance of the platform, including on-call periods.
}
\cventry{2005--2006}{Junior Developer}{Nothing but Net Ltd.}{}{}{
My work here allowed me to grow my programming experience from what I had learned at University, the main programming language was Java. I administered their internal and external network infrastructure including web application deployment and other services such as mail. I also was sponsored to work for the NZ Open Source Society.
}
\cventry{2002-2006}{IT Consultant}{Manuka Primary School}{}{}{
My work with Manuka Primary School involved developing solutions to their needs from low-cost components and network administration. In developing their Intranet system I gained knowledge of content and management, workflow and systems integration.
}

\section{Education}
\cventry{2002--2006}{Bachelor of Science, Computer Science}{Massey University}{Albany, Auckland}{}{
Papers include: Technical Writing, GUI Programming, Functional Programming, Computer Architecture, Enterprise Software Architecture
}
\cventry{2006}{Bursary}{Glenfield College}{Auckland}{}{
Also achieved: Higher School Certificate, Sixth Form Certificate and School Certificate
}

\section{Technical Experience}
\subsection{Extremely Proficient With}
\cvline{languages}{Python, PHP, SQL, BASH, Puppet, HTML, CSS}
\cvline{technologies}{GNU/Linux, Zend Framework, MySQL, Symfony \& Silex, Vim, HTTP, Low-level Networking}
\subsection{Have Experience With}
\cvline{languages}{Java, C, Objective C, C++}
\cvline{technologies}{Nginx, Javascript, Django, Pyramid, Twisted, Solr, Servlets}

\section{References}
\cvline{}{References available upon request}

\end{document}
